%\documentclass[12pt,preprint]{aastex}
\documentclass[apjl]{emulateapj}

\pdfoutput=1

\usepackage{comment}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{multirow}
\usepackage{wasysym}
\usepackage{subfigure}
\usepackage{epsfig}
\usepackage{color}
\definecolor{linkcolor}{rgb}{0,0,0.5}
\usepackage[%
	colorlinks=true,	% false: boxed links; true: colored links
	pdfpagelabels=true,
	hypertexnames=true,
	plainpages=false,
	naturalnames=true,
%	bookmarks=true,         % show bookmarks bar?
%	unicode=false,          % non-Latin characters in Acrobat’s bookmarks
%	pdftoolbar=true,        % show Acrobat’s toolbar?
%	pdfmenubar=true,        % show Acrobat’s menu?
%	pdffitwindow=false,     % window fit to page when opened
%	pdfstartview={FitH},    % fits the width of the page to the window
	pdftitle={Priors for Orbital Eccentricity},    % title
	pdfauthor={David M. Kipping},     % author
%	pdfsubject={Subject},   % subject of the document
%	pdfcreator={Creator},   % creator of the document
%	pdfproducer={Producer}, % producer of the document
%	pdfkeywords={keyword1} {key2} {key3}, % list of keywords
%	pdfnewwindow=true,      % links in new window
	urlcolor=linkcolor,     % color of external links
	linkcolor=linkcolor,    % color of internal links (change box color with linkbordercolor)
	citecolor=linkcolor,    % color of links to bibliography
	filecolor=linkcolor,    % color of file links
        ]{hyperref}
%

% #############################################################################
% Specific latex definitions for this paper

\input{shortcuts.tex}

%% #############################################################################

%% VARIABLE DEFINITIONS
%%
\newboolean{emulateapj}
\setboolean{emulateapj}{true}

\newboolean{astroph}
\setboolean{astroph}{true}

\newboolean{png}
\setboolean{png}{false}

\newboolean{color}
\setboolean{color}{true}

%% ############################################################################

\shortauthors{Angus \& Kipping}
\shorttitle{Probabilistic Inference of Stellar Parameters}
\ifthenelse{\boolean{emulateapj}}{
    \newcommand{\titledag}{$\dagger$}
}{
    \newcommand{\titledag}{\dagger}
}
\def\mathbi#1{\textbf{\em #1}}

\begin{document}

%% Titlepage
\title {Probabilistic Inference of Basic Stellar Parameters:\\
Application to Flickering Stars %to Surface Gravity and Mean Density
\altaffilmark{\titledag}}

%% Authors
\author{
	{\bf	Ruth~Angus\altaffilmark{1,2},
		David.~M.~Kipping\altaffilmark{2,3},
	}
}

\altaffiltext{1}{Dept. of Physics, University of Oxford, UK; email:
		 ruth.angus@astro.ox.ac.uk}

\altaffiltext{2}{Harvard-Smithsonian Center for Astrophysics,
		Cambridge, MA 02138, USA; email: dkipping@cfa.harvard.edu}

\altaffiltext{3}{Department of Astronomy, Columbia University, 550 W 120th St.,
                 New York, NY 10027, US}

\altaffiltext{$\dagger$}{
%%
Based on archival data of the \Kepler\ telescope.
}


%% EOF authors

% #####################################################################
%% abstract
\begin{abstract}

% aims
The relations between observable stellar parameters are usually assumed to be
deterministic.
That is, given an infinitely precise measurement of independant
variable, `$x$', and some model, the value of dependant variable, `y' can be
known exactly.
In practise this assumption is rarely valid and intrinsic stochasticity means
that two stars with exactly the same `$x$', will have slightly different
`$y$'s.
% methods
The relation between short-timescale brightness fluctuations (flicker) of stars
and both surface gravity \citep{bastien:2013} and stellar density
\citep{kipping:2014} are two such stochastic relations that have, until now,
been treated as deterministic ones.
We recalibrate these relations in a probabilistic framework, using
Hierarchical Bayesian Modelling (HBM) and constrain the instrinsic scatter in
the relations.
Our treatment also fully accounts for the observational uncertainties on all
variables.
% results
We find evidence for additional scatter in the relationships, that cannot be
accounted for by the observational uncertainties alone.
This intrinsic scatter increases with decreasing flicker, i.e. there is more
additional scatter for subgiants than for dwarfs, suggesting that the flicker
relationships are equally (if not more) valid for dwarf stars.

\end{abstract}

% #####################################################################
%% keywords
\keywords{
%%
	stars: fundamental parameters --- techniques: photometric ---
        methods: statistical
%%
}

%% EOF keywords
%% EOF titlepage

% #####################################################################
%% Introduction
\section{INTRODUCTION}
\label{sec:intro}

\input{introduction.tex}

\section{PROBABILISTIC CALIBRATION}
\label{sec:HBM}

\input{HBM.tex}

\section{DISCUSSION}
\label{sec:discussion}

\input{discussion.tex}

% #####################################################################
%% Acknowledgements
\acknowledgements
\section*{Acknowledgements}

RA would like to thank Dan Foreman-Mackey for his extremely helpful suggestions
and comments, and Angie Wolfgang and John Johnson for their fantastic advice.
RA would also like to thank the SAMSI institute and the other members of the
SAMSI {\it Kepler} exoplanet statistics working groups.
DMK thanks...

%% EOF Acknowledgements

% #####################################################################
%% Bibliography
\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Andrieu \& Roberts}{2009}]{andrieu:2009}
Andrieu, C., \& Roberts, G.~O., Ann. Statist., 2, 695
\bibitem[\protect\citeauthoryear{Angus et al.}{2015}]{angus:2015}
Angusr, R., Aigrain, S., Foreman-Mackey, D. \& McQuillan, A., 2015, MNRAS,
450, 1787
\bibitem[\protect\citeauthoryear{Bastien et al.}{2013}]{bastien:2013} Bastien,
F. A., Stassun, K. G., Basri, G. \& Pepper, J., 2013, Nature, 500, 427
\bibitem[\protect\citeauthoryear{Chaplin et al.}{2014}]{chaplin:2014}
Chaplin, W.~J., Basu, S., Huber, D. et al., 2014, ApJS, 210, 1
\bibitem[\protect\citeauthoryear{Cranmer et al.}{2014}]{cranmer:2014}
Cranmer, S. R., Bastien, F. A., Stassun, K. G. \& Saar, S. H., 2014, ApJ, 781,
124
\bibitem[\protect\citeauthoryear{Foreman-Mackey et al.}{2014}]
{foreman-mackey:2014} Foreman-Mackey, D., Hogg, D.~W. \& Morton, T.~D., 2014,
ApJ, 795, 64
\bibitem[\protect\citeauthoryear{Fox}{1997}]{fox:1997}
Fox, J., 1997, Applied Regression Analysis, Linear Models, and Related Methods
(Thousand Oaks:Sage Publications, Inc.)
\bibitem[\protect\citeauthoryear{Fuller}{1987}]{fuller:1987}
Fuller, W.~A., 1987, Wiley Series in Probability and Mathematical Statistics
\bibitem[\protect\citeauthoryear{Hogg et al.}{2010}]{hogg:2010}
Hogg, D.~W., Myers, A.~D. \& Bovy, J., 2010, ApJ, 725,
2166
\bibitem[\protect\citeauthoryear{Huber et al.}{2013}]{huber:2013}
Huber, D., Chaplin, W.~J., Christensen-Dalsgaard, J. et al., 2013, ApJ, 767,
127
\bibitem[\protect\citeauthoryear{Kelly}{2007}]{kelly:2007} Kelly, B.~C., 2007,
ApJ, 665, 1489
\bibitem[\protect\citeauthoryear{Kipping et al.}{2014}]{kipping:2014}
Kipping, D.~M., Bastien, F.~A., Stassun, K.~G., Chaplin, W.~J., Huber, D. \&
Buchhave, L.~A., 2014, ApJ, 785, 32
\bibitem[\protect\citeauthoryear{Rogers}{2015}]{rogers:2015}
Rogers, L.~A., 2015, ApJ, 801, 41
\bibitem[\protect\citeauthoryear{Seager \& Mall\'{e}n-Ornelas}{2003}]
{seager:2003}Seager, S., \& Mall\'{e}n-Ornelas, G., 2003, ApJ, 585, 1038
\bibitem[\protect\citeauthoryear{Wolfgang et al.}{2015}]{wolfgang:2015}
Wolfgang, A., Rogers, L.~A., Ford, E.~B., 2015, ApJ, submitted
(astro-ph:1504.07557)
\end{thebibliography}

\end{document}

%% EOF document

